\chapter{Procedure week 1\cite{skript_ballmoos}}

The listed steps are based on the provided script, with changes where we
deviated from what was written.

\section{Expression}

Expression was done by the assistants ahead of time, the corresponding steps of
the protocol are only listed for completeness' sake.

\begin{itemize}
	\item From a freshly transformed plate (plasmid: pET28) of the given
		membrane protein target in BL21 pLysS strain, inoculate
		\SI{30}{\ml} LB medium containing \SI{30}{\ug \per \ml}
		kanamycin (kan) for the expression of different proteins. Leave
		shaking overnight (ON) at \SI{37}{\celsius}. This pre-culture
		volume is suitable for \SI{1.5}{\l} culture grow-up.

	\item Prepare and autoclave \SI{1.5}{\l} of LB medium overnight so that
		the medium remains warm on the next day.

	\item To each \SI{1.5}{\l} bottle, add \SI{30}{\ml} of pre-culture
		inoculum, the appropriate antibiotics and incubate in a water
		bath with a controlled temperature at \SI{37}{\celsius}. We
		used a new device called LEX48 for bacteria growing in which
		shaking is replaced by air bubbling directly in the medium.

	\item Check the OD$_{\SI{600}{\nm}}$ from time to time and induce
		expression once the latter reached \numrange{1.2}{1.5} by adding
		\SI{0.2}{\milli\Molar} of IPTG (Isopropyl
		$\beta$-D-1-thiogalactopyranoside).

	\item Harvest bacterial cells 5h after induction by spinning down at
		\SI{8000}{\rpm} for \SI{15}{\min}. Discard supernatant, wash
		the pellet once with \SI{50}{\milli\Molar} HEPES pH 7.5,
		\SI{200}{\milli\Molar} \ce{NaCl}, \SI{7.5}{\percent} glycerol
		then flash-freeze in liquid nitrogen and store at
		\SI{-80}{\celsius} for further use.
\end{itemize}

In parallel, we transformed E. coli LEMO21 (DE3) strain with the plasmid
pET28-cybB561-dsred.

\begin{itemize}
	\item Plate the cells on an LB agar plate containing kanamycin and
		chloramphenicol and incubate them overnight at \SI{37}{\celsius}
\end{itemize}


\section{Isolation of membranes}

\begin{table}
	\centering
	\begin{tabu}{llll}
		\toprule
		Component & Stock & Final concentration & Used amount \\
		\midrule
		HEPES & \SI{1}{\Molar} & \SI{50}{\milli\Molar} & \SI{12.5}{\ml} \\
		Glycerol & \SI{85}{\percent} & \SI{7.5}{\milli\Molar} & \SI{22}{\ml} \\
		\ce{NaCl} & \SI{58.44}{\g \per \mole} & \SI{200}{\milli\Molar} & \SI{2.92}{\g} \\
		dd\ce{H2O} & & & To \SI{250}{\ml} \\
		\bottomrule
	\end{tabu}
	\caption{\SI{50}{\milli\Molar} HEPES buffer}
	\label{tbl:hepes_buffer}
\end{table}

\begin{table}
	\centering
	\begin{tabu}{lll}
		\toprule
		Dilution & Sample & dd\ce{H2O} \\
		\midrule
		1 : 5 & \SI{12}{\ul} & \SI{48}{\ul} \\
		1 : 10 & \SI{6}{\ul} & \SI{54}{\ul} \\
		1 : 20 & \SI{3}{\ul} & \SI{57}{\ul} \\
		1 : 40 & \SI{1.5}{\ul} & \SI{58.5}{\ul} \\
		\bottomrule
	\end{tabu}
	\caption{Sample dilutions for BCA assay}
	\label{tbl:bca_dilutions}
\end{table}

\begin{table}
	\centering
	\begin{tabu}{llll}
		\toprule Vial & Diluent & BSA & Final BSA concentration \\
		\midrule
		A & \SI{0}{\ul}   & \SI{300}{\ul} stock  & \SI{2000}{\ug\per\ml} \\
		B & \SI{125}{\ul} & \SI{375}{\ul} stock  & \SI{1500}{\ug\per\ml} \\
		C & \SI{325}{\ul} & \SI{325}{\ul} stock  & \SI{1000}{\ug\per\ml} \\
		D & \SI{175}{\ul} & \SI{175}{\ul} vial B & \SI{750}{\ug\per\ml} \\
		E & \SI{325}{\ul} & \SI{325}{\ul} vial C & \SI{500}{\ug\per\ml} \\
		F & \SI{325}{\ul} & \SI{325}{\ul} vial E & \SI{250}{\ug\per\ml} \\
		G & \SI{325}{\ul} & \SI{325}{\ul} vial F & \SI{125}{\ug\per\ml} \\
		H & \SI{400}{\ul} & \SI{100}{\ul} vial G & \SI{25}{\ug\per\ml} \\
		I & \SI{400}{\ul} & \SI{0}{\ul}          & \SI{0}{\ug\per\ml} \\
		\bottomrule
	\end{tabu}
	\caption{Standard dilutions for BCA assay}
	\label{tbl:bca_standard}
\end{table}

We worked with a bacterial pellet, weighing \SI{6.4}{\g}, containing the H158F
mutant of the superoxide oxidase.

\begin{itemize}
	\item A HEPES buffer according to table \ref{tbl:hepes_buffer} was
		prepared, the bacterial pellet thawed, and resuspended in
		\SI{32}{\ml} buffer. The resulting volume was roughly
		\SI{40}{\ml}.
	\item \SI{0.2}{\ml} of a \SI{0.2}{\Molar} PMSF stock was added for a
		final concentration of \SI{1}{\milli\Molar}
	\item \SI{0.8}{\ml} of a \SI{0.1}{\Molar} \ce{MgCl2} stock solution was
		added for a final concentration of \SI{2}{\milli\Molar}
	\item A tiny spatula tip DNAse, half a spoon lysozyme, and half a spoon
		PEFA-block were added.
	\item Bacterial cells were broken in the maximator at a pressure of $>$
		\SI{1000}{\bar}, three passes.
	\item The sample was centrifuged for \SI{15}{\min} at \SI{8000}{G} to
		remove unbroken cells and debris. The supernatant was
		transferred to a new tube, the pellet discarded. 
	\item The sample was centrifuged for \SI{5}{\min} at \SI{8000}{G} once
		more, the supernatant transferred to a new tube and the pellet
		discarded.
	\item The sample was ultracentrifuged for \SI{45}{\min} at $>$
		\SI{186000}{G} and \SI{4}{\celsius}. The supernatant was
		discarded.
	\item The pellet was resuspended in \SI{4}{\ml} HEPES buffer and
		homogenized.
	\item \SI{50}{\ul} of the sample were put aside for future use.
	\item Four dilutions according to table \ref{tbl:bca_dilutions} were
		prepared.
	\item The BCA working reaction was prepared by another group.
	\item Four tubes were prepared, each containing \SI{50}{\ul} of one of
		the dilutions and \SI{950}{\ul} of the BCA working reaction.
	\item The BCA assays were incubated for \SI{15}{\min} at \SI{37}{\celsius}
	\item A standard curve based on BSA was prepared by another group,
		according to table \ref{tbl:bca_standard}.
	\item The absorption of the dilutions and the standard curve at
		\SI{562}{\nm} was measured. % TODO link table?
\end{itemize}

\section{Preparation of transformed pre-culture}

The following steps were performed by another group, and are listed for
completeness' sake.

\begin{itemize}
	\item Pick 3 colonies from a freshly transformed plate with plasmid
		pET28a-cybB561-dsred of the given membrane protein target in
		Lemo21 (DE3) strain and inoculate \SI{15}{\ml} LB-medium
		containing \SI{35}{\ug \per \ml} of kanamycin (kan) and
		\SI{25}{\ug \per \ml} of chloramphenicol.
	\item Leave shaking overnight (ON) at \SI{37}{\celsius}. This volume is
		suitable for optimization of protein expression experiments
		(day 2)
\end{itemize}

In addition, medium according to tables \ref{tbl:medium_lb},
\ref{tbl:medium_tb_1}, \ref{tbl:medium_tb_2}, \ref{tbl:medium_auto_basis} and
\ref{tbl:medium_auto_stock} were prepared.

The LB medium was autoclaved. Part 1 of the TB medium was autoclaved, part 2
filtered. Both parts of the auto-inducing medium had their pH set to 7 with
\ce{NaOH}, the basis was then autoclaved and the stock filtered. All medium was
then set aside for the next day.

\begin{table}
	\centering
	\begin{tabu}{llll}
		\toprule
		Component & Stock & Final concentration & Used amount \\
		\midrule
		Tryptone & & \SI{1}{\percent} & \SI{2}{\g} \\
		Yeast extract & & \SI{0.5}{\percent} & \SI{1}{\g} \\
		\ce{NaCl} & & \SI{0.5}{\percent} & \SI{1}{\g} \\
		\ce{H2O} & & & To \SI{200}{\ml} \\
		\bottomrule
	\end{tabu}
	\caption{LB medium}
	\label{tbl:medium_lb}
\end{table}

\begin{table}
	\centering
	\begin{tabu}{llll}
		\toprule
		Component & Stock & Final concentration & Used amount \\
		\midrule
		Tryptone & & \SI{1.2}{\percent} & \SI{2.4}{\g} \\
		Yeast extract & & \SI{2.4}{\percent} & \SI{4.8}{\g} \\
		\ce{H2O} & & & To \SI{180}{\ml} \\
		\bottomrule
	\end{tabu}
	\caption{TB medium part 1}
	\label{tbl:medium_tb_1}
\end{table}

\begin{table}
	\centering
	\begin{tabu}{llll}
		\toprule
		Component & Stock & Final concentration & Used amount \\
		\midrule
		\ce{KH2PO4} & & \SI{17}{\milli\Molar} & \SI{0.46}{\g} \\
		\ce{K2HPO4} & & \SI{72}{\milli\Molar} & \SI{1.25}{\g} \\
		\ce{Glycerol} & \SI{85}{\percent} & \SI{0.5}{\percent} & \SI{588}{\ul} \\
		\ce{H2O} & & & To \SI{20}{\ml} \\
		\bottomrule
	\end{tabu}
	\caption{TB medium part 2}
	\label{tbl:medium_tb_2}
\end{table}

\begin{table}
	\centering
	\begin{tabu}{llll}
		\toprule
		Component & Stock & Final concentration & Used amount \\
		\midrule
		Tryptone & & \SI{1}{\percent} & \SI{2}{\g} \\
		Yeast extract & & \SI{0.5}{\percent} & \SI{1}{\g} \\
		\ce{H2O} & & & To \SI{180}{\ml} \\
		\bottomrule
	\end{tabu}
	\caption{Auto-inducing medium basis}
	\label{tbl:medium_auto_basis}
\end{table}

\begin{table}
	\centering
	\begin{tabu}{llll}
		\toprule
		Component & Stock & Final concentration & Used amount \\
		\midrule
		\ce{Na2HPO4} & & \SI{500}{\milli\Molar} & \SI{2.67}{\g} \\
		\ce{KH2PO4} & & \SI{500}{\milli\Molar} & \SI{2.04}{\g} \\
		\ce{(NH4)2SO4} & & \SI{250}{\milli\Molar} & \SI{1}{\g} \\
		\ce{MgSO4} & \SI{1}{\Molar} & \SI{20}{\milli\Molar} & \SI{600}{\ul} \\
		\ce{Glycerol} & \SI{85}{\percent} & \SI{5}{\percent} & \SI{1.76}{\ml} \\
		\ce{Glucose} & & \SI{0.5}{\percent} & \SI{0.16}{\g} \\
		\ce{Lactose} & & \SI{2}{\percent} & \SI{0.6}{\g} \\
		\ce{H2O} & & & To \SI{30}{\ml} \\
		\bottomrule
	\end{tabu}
	\caption{Auto-inducing medium 10x stock}
	\label{tbl:medium_auto_stock}
\end{table}


\section{Transformation of bacterial cells}

\begin{itemize}
	\item \SI{50}{\ul} of \ce{CaCl2} treated competent cells were mixed
		with \SI{1}{\ul} of pET28-cybB561 plasmids and incubated on ice
		for \SI{30}{\min}.
	\item The mixture was heat-shocked for \SI{1}{\min} at
		\SI{42}{\celsius}, then incubated on ice for \SI{5}{\min}.
	\item \SI{0.5}{\ml} LB medium, pre-warmed to \SI{37}{\celsius}, was
		added.
	\item The mixture was incubated for \SI{1}{\hour} at \SI{37}{\celsius}.
	\item The transformed bacteria were spread on a LB plate containing
		\SI{30}{\ug\per\ml} kanamycin.
	\item The plate was incubated overnight at \SI{37}{\celsius}.
	\item On the next day bacterial growth was observed on the plate,
		indicating that the transformation had been successful. The
		plate was then discarded.
\end{itemize}

\section{Expression screening of E. coli cells}

\begin{itemize}
	\item The two parts of the TB and auto-inducing medium respectively
		were mixed.
	\item Antibiotics were added to all media.
		\begin{itemize}
			\item \SI{200}{\ul} kanamycin of a \SI{35}{\mg\per\ml}
				stock for a final concentration of
				\SI{35}{\ug\per\ml}.
			\item \SI{200}{\ul} chloramphenicol of a
				\SI{25}{\mg\per\ml} stock for a final
				concentration of \SI{25}{\ug\per\ml}.
		\end{itemize}
	\item \SI{1}{\ml} of each medium was set aside for use as a blank.
	\item Samples according to table \ref{tbl:expression_samples} were
		prepared.
		\begin{itemize}
			\item All samples had \SI{15}{\ml} of its corresponding
				medium, and \SI{800}{\ul} of the preculture
				added.
			\item All Rha+ samples had \SI{37.5}{\ul} of a
				\SI{0.1}{\Molar} Rhamnose stock solution added,
				for a final concentration of
				\SI{0.25}{\milli\Molar}.
		\end{itemize}
	\item Samples were incubated at \SI{37}{\celsius}, and their OD$_{600}$
		measured every \SIrange{30}{60}{\min} until their absorbance had
		reached $0.5$.

		The measurement at \SI{90}{\min} was later found to be
		incorrect due to the cuvette having been inserted the wrong
		way.

	\item After \SI{90}{\min} all IPTG+ samples had \SI{13}{\ul} of a
		\SI{0.2}{\Molar} stock solution added.
	\item Samples were incubated at \SI{37}{\celsius} for another
		\SI{200}{\min}, and had their OD$_{600}$ measured every
		\SIrange{30}{90} minutes. The volume used to measure the
		absorbance of the LB samples was subsequently centrifuged, and
		the size and colour of the pellet observed.
	\item After \SI{290}{\min} \SI{198}{\ul} of the culture were
		solubilized with \SI{2}{\ml} of a \SI{10}{\percent} SDS stock
		solution in a 96-well plate. The fluorescence was measured with
		a plate reader to determine the amount of expressed protein. The
		measurements for the LB samples were redone, as they had been
		contaminated while being added to the well.
% TODO: Link table with measurements?
\end{itemize}

\begin{table}
	\centering
	\begin{tabu}{lll}
		\toprule
		Medium & Rhamnose & IPTG \\
		\midrule
		LB & - & - \\
		LB & + & - \\
		LB & - & + \\
		LB & + & + \\

		TB & - & - \\
		TB & + & - \\
		TB & - & + \\
		TB & + & + \\

		ZYM-505 & - & - \\
		ZYM-505 & + & - \\
		ZYM-505 & - & + \\
		ZYM-505 & + & + \\
		\bottomrule
	\end{tabu}
	\caption{Samples for protein expression screening}
	\label{tbl:expression_samples}
\end{table}
