\documentclass[a4paper]{scrartcl}

% Uncomment to optimize for double-sided printing.
% \KOMAoptions{twoside}

% Set binding correction manually, if known.
% \KOMAoptions{BCOR=2cm}

% Localization options
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% Quotations
\usepackage{dirtytalk}

% Enhanced verbatim sections. We're mainly interested in
% \verbatiminput though.
\usepackage{verbatim}

% PDF-compatible landscape mode.
% Makes PDF viewers show the page rotated by 90°.
\usepackage{pdflscape}

% Subfigures
\usepackage{subcaption}

% Figures at end (of chapter via \processdelayedfloats)
% \usepackage[figuresonly,nomarkers,nofiglist]{endfloat}

% Advanced tables
\usepackage{tabu}
\usepackage{longtable}

% Fancy tablerules
\usepackage{booktabs}

% Graphics
\usepackage{graphicx}

% Current time
\usepackage[useregional=numeric]{datetime2}

% Float barriers.
% Automatically add a FloatBarrier to each \section
\usepackage[section]{placeins}

% Importing CSV into tables
\usepackage{csvsimple}

% Custom header and footer
\usepackage{fancyhdr}

\usepackage{geometry}
\usepackage{layout}

% Math tools
\usepackage{mathtools}
% Math symbols
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{amsthm}

\DeclarePairedDelimiter\abs{\lvert}{\rvert}

\pagestyle{plain}
% \fancyhf{}
% \lhead{}
% \lfoot{}
% \rfoot{}
% 
% Source code & highlighting
\usepackage{listings}

% SI units
\usepackage[binary-units=true]{siunitx}
\DeclareSIUnit\Molar{\textsc{m}}
\DeclareSIUnit\Da{\textsc{Da}}
\DeclareSIUnit\mole{mol}
\DeclareSIUnit\rpm{rpm}
\DeclareSIUnit\cfu{cfu}

\usepackage{mhchem}

\newcommand{\mysubject}{2115 - Lab course biochemistry 2}
\newcommand{\mytitle}{Expression, purification and characterization of superoxide oxidase SOO}

% Convenience commands
\newcommand{\mailsubject}{\mysubject{} \mytitle{}}
\newcommand{\maillink}[2]{\href{mailto:#1?subject=\mailsubject}
                               {#2}}

% Should use this command wherever the print date is mentioned.
\newcommand{\printdate}{\today}

\subject{2115 - Lab course biochemistry 2}
\title{Expression, purification and characterization of superoxide oxidase `SOO'}
\subtitle{Final report}
\author{\maillink{michael.senn@students.unibe.ch}{Michael Senn} - 16-126-880}

\date{\printdate}

\publishers{von Ballmoos group, University of Bern\\Abbas Maxime Abou Hamdan \& Sabina Deutschmann}

% Needs to be the last command in the preamble, for one reason or
% another. 
\usepackage{hyperref}

\begin{document}
\maketitle

\begin{abstract}
	Three variants of superoxide oxidase were grown in bacterial BL21 cells
	and purified using size-exclusion and affinity chromatography.
	Purification efficiency was monitored using fluorescence of
	dsRed-tagged proteins.

	Purified enzymes were reconstituted into liposomes using freeze-thaw
	cycles. Reconstituted and solubilzed enzymes were then analyzed,
	measuring their reduction in presence of superoxide or quinone, as well
	as enzymatic activity using absorbance measurements.

	Using the collected data the enzymes were characterized, estimating
	their $K_m$ value as well as gaining insights into the orientation of
	enzymes in liposomes.
\end{abstract}

\newpage
\part*{Introduction}

Reactive oxygen species (`ROS') such as superoxide (\ce{O2-}) or hydrogen
peroxide (\ce{H2O2}) are toxic to the body, causing damage to proteins or DNA,
with links to various diseases including cancer. As such organisms under
aerobic conditions counteract ROS via eg Superoxide Dismutase (`SOD') which
catalyzes the partitioning of superoxide into molecular oxygen and hydrogen
peroxide.

One major source of superoxide is the oxidative phosphoryliation within the
mitochondrial matrix. \cite{Novo2008} To a lesser extent these superoxides
diffuse into the cytoplasm, where they are acted upon by SOD. A significant
portion of superoxides however is oxidised by superoxide oxidases - henceafter
referred to as `SOO' or `Halonsaft' due to its colour - a family of
membrane-bound proteins which oxidize superoxides.\cite{superoxide_salvaging}.

One protein of this family is CybB from E. Coli which was shown to function as
a superoxide:ubiquinone oxidoreductase. It oxidizes superoxide to oxygen while
simultaneously reducing quinone to quinol.\cite{superoxide_salvaging} This
enzymatic activity both serves to remove superoxides in close proximity to the
cell membrane, as well as restore the quinone pool, helping to save energy.

% TODO
% - Characterizing (eg activity) we did?

\newpage
\part*{Material \& methods}

\newpage
\part*{Results \& discussion}

\newpage
\part*{Conclusion}



\bibliographystyle{plain}
\bibliography{references}

\end{document}
