\twocolumn

\part{Material \& methods}

\section{Transformation \& expression}

Transformation and expression were done as described.
\cite{superoxide_salvaging}. Summarily, \ce{CaCl2} treated cells were mixed
with pET28-cybB561 plasmids, and heat shock treated (\SI{30}{\min} on ice,
\SI{1}{\min} at \SI{42}{\celsius}, \SI{5}{\min} on ice, \SI{1}{\hour} at
\SI{37}{\celsius} shaking at \SI{900}{rpm}), then incubated overnight at
\SI{37}{\celsius} with \SI{30}{\ug\per\ml} Kanamycin. Transformed colonies were
picked and inoculated overnight at \SI{37}{\celsius} in LB medium with
\SI{30}{\ug\per\ml} Kanamycin and \SI{35}{\ug\per\ml} Chloramphenicol.

% TODO: Antibiotic amounts correct? Check lab journal

\section{Membrane isolation \& enzyme purification}

Purification of SOO was done as described. \cite{superoxide_salvaging}.

In summary, resuspended bacterial cells were broken open and DNASE-treated in a
maximator (3 passes at $>$\SI{1000}{\bar}). Pelleted membranes were resuspended
in \SI{50}{\milli\Molar} HEPES pH 7.4, \SI{200}{\milli\Molar} \ce{NaCl},
\SI{7.5}{\percent} glycerol buffer. Protein concentration was determined with a
BCA assay.

Membranes were solubilized in \SI{1}{\percent} OGNG \SI{1}{\milli\Molar} PMSF
and stirred at \SI{4}{\celsius} for \SI{1}{\hour}. Insolubilized membranes were
pelleted at \SI{150000}{g} for \SI{45}{\min}. The supernatant was loaded on a
\ce{Ni^{2+}} column with column volume \SI{1}{\ml} and incubated for
\SI{45}{\min} at \SI{4}{\celsius} on a rotating wheel. The column was then
washed and eluted with \SI{5}{\milli\Molar} and \SI{100}{\milli\Molar}
Histidine.

Parts of \hsdsred{} were treated overnight with TEV-protease, and a reverse
\ce{Ni^{2+}} IMAC performed, with elution with \SI{100}{\milli\Molar}
Histidine.

The eluate was concentrated to \SI{0.5}{\ml} with a \SI{10}{\kilo\Da}
concentrator, and loaded onto a S200 increase 10/300 column. Fractions
suspected to contain the protein were pooled. Protein concentration was
determined via absorbance measurement of oxidised and reduced form (via addition
of DTT) between \SIrange{600}{400}{\nm}.

Aliquots of the purification steps were loaded onto a \SI{12}{\percent}
SDS-PAGE gel, ran at \SI{125}{\V} for \SI{20}{\min} and \SI{185}{\V} for
\SI{80}{\min}. The gel was stained with coomassie.

Efficiency of purification was measured via fluorescence measurement of
\hsdsred{} at an emission of \SI{586}{\nm} and extinction of \SI{555}{\nm}.

\section{Enzyme characterization}

Characterization was performed according to the same Nature
article\cite{superoxide_salvaging}.

Dried lipids were resuspended in \SI{20}{\milli\Molar} HEPES pH 7.4,
\SI{20}{\milli\Molar} \ce{KCl}, \SI{200}{\milli\Molar} \ce{NaCl}. Unilamellar
liposomes were formed by freeze-thaw cycles in nitrogen and \SI{29.4}{\celsius}
respectively, followed by sonication (\SI{2.5}{\min}, cycles of \SI{0.5}{\min}
on \SI{0.5}{\min} off).

CybB was reconstituted by adding enzymes to liposomes with \SI{0.6}{\percent}
sodium cholate. Detergent was removed by loading the sample on a P10 gel
filtration column and eluting it.

Reduction of CybB was measured via absorption measurement at \SI{428}{\nm}. In
a first set \SI{1}{\micro\Molar} of solubilized enzyme was mixed with
\SI{20}{\milli\Molar} HEPES pH 7.4, \SI{20}{\milli\Molar} \ce{KCl},
\SI{200}{\milli\Molar} \ce{NaCl}, \SI{0.05}{\percent} DDM for a final reaction
volume of \SI{750}{\ul}. At t=\SI{1}{\min} \SI{1}{\ul} substrate (quinol or
superoxide via Xanthyloxidase) was added, at t=\SI{3}{\min} the enzyme was
fully reduced via DTT. In a second set the same experiment was performed with
\SI{10}{\ul} reconstituted enzymes in equal fashion except a buffer without
detergent was used. The two sets were done for both the wildtype as well as the
mutant.

Fluorescence of reconstituted and solubilized, cleaved and uncleaved \hsdsred{}
was measured at an excitation of \SI{555}{\nm} and emission of \SI{595}{\nm}.
Fluorescence was quenched with \SI{1}{\milli\Molar} \ce{Cu2+} and restored with
\SI{10}{\milli\Molar} EDTA.

Activity of solubilized enzymes was determined by measuring reduction of WST-1
via absorption at \SI{455}{\nm}. In a first set \SI{100}{\micro\Molar} quinone,
\SI{60}{\nano\Molar} BO3 oxidase and buffer (\SI{100}{\milli\Molar} sodium
phosphate pH 8, \SI{0.1}{\milli\Molar} DTPA, \SI{0.1}{\milli\Molar}
Hypoxanthine, \SI{0.05}{\percent} DDM) for a final volume of \SI{750}{\ul} were
mixed. At t=\SI{0.5}{\min} \SI{0.03}{U} XO, at t=\SI{1.5}{\min} varying volumes
of enzyme were added. Enzyme concentration was increased until quenching of
superoxide production was level with a reference measurement done using
superoxide dismutase.

In a second set the determined concentration of enzyme was kept constant while
quinone concentration was varied.
